Qualitative Probabilistic Programming

### 2015-06-05 paper/paper.tex
cleaned up models

  \subsection{Clustering}
{\small
\begin{lstlisting}
var nclusters = 3;
var dim = 2;

var n = 100;

var Point = Vector(3, Double);
var Cluster = Categorical(3);
var getPoint = randFunction(Cluster, Point);
return function() {
  return repeat(n, function(i) {
    var cluster = randomValue(Cluster);
    observe(getPoint, cluster);
  });
};
\end{lstlisting}
}

@@

{\small
\begin{lstlisting}
var n = 50;

var Class = Categorical(2);
var Features = Vector(10, Bool);

var classFeatures = [randFunction(Features), randFunction(Features)];

return function() {
  repeat(n, function(i) {
    var whichClass = randomValue(Class);
    observe(classFeatures, whichClass);
  });
};
\end{lstlisting}
}

@@

  \subsection{Factor analysis}
{\small
\begin{lstlisting}

var nfactors = 2;
var dim = 4;

var n = 50;

var Factors = Vector(2, Double);
var Point = Vector(5, Double);
var getPoint = randFunction(Factors, Point);

return function() {
  return repeat(n, function(i) {
    var factors = randomValue(Factors);
    observe(getPoint, factors);
  });
};
\end{lstlisting}
}

@@

  \subsection{Hidden Markov model}
{\small
\begin{lstlisting}

var chainLength = 20;

var n = 10;

var State = Categorical(2);
var Obs = Categorical(4);
var transFun = randFunction(State, State);
var obsFun = randFunction(State, Obs);

@@

return function() {
  return repeat(n, function(sampIndex) {
    observeStates(randomValue(State), 0);
  });
};
\end{lstlisting}
}

@@

\subsection{Latent Dirichlet allocation}
{\small
\begin{lstlisting}

var maxWordsPerDocument = 100;
var nDocuments = 20;

var Class = Categorical(3);
var Word = Categorical(10);
var classToWord = randFunction(Class, Word);

return function() {
  return repeat(nDocuments, function() {
    var whichClass = randomValue(Class);
    var nWords = observe(randomIntegerERP, maxWordsPerDocument);
    repeat(nWords, function(wordIndex) {
      observe(classToWord, whichClass);
    });
    return whichClass;
  });
};

\end{lstlisting}
}

@@

{\small
\begin{lstlisting}

var Input = Categorical(30);
var Hidden = Categorical(10);
var Output = Categorical(2);

var inputs = [...];

@@

return function() {
  return repeat(inputs.length, function(sampIndex) {
    var hiddenLayer = inputToHidden(inputs[sampIndex]);
    observe(hiddenToOutput, hiddenLayer);
  });
};
\end{lstlisting}
}

>>>>

  \subsection{Clustering}
{\small
\begin{lstlisting}
var Cluster = Categorical(3);
var Point = Vector(2, Double);
var getPoint = randFunction(Cluster, Point);

var model = function() {
  var cluster = randomValue(Cluster);
  observe(getPoint, cluster);
};
\end{lstlisting}
}

@@

{\small
\begin{lstlisting}
var Class = Categorical(2);
var Features = Vector(10, Bool);
var classFeatures = [randFunction(Features), randFunction(Features)];

var model = function() {
  var whichClass = randomValue(Class);
  observe(classFeatures, whichClass);
};
\end{lstlisting}
}

@@

  \subsection{Factor analysis}
{\small
\begin{lstlisting}
var Factors = Vector(2, Double);
var Point = Vector(5, Double);
var getPoint = randFunction(Factors, Point);

var model = function() {
  var factors = randomValue(Factors);
  return observe(getPoint, factors);
};
\end{lstlisting}
}

@@

  \subsection{Hidden Markov model}
{\small
\begin{lstlisting}
var chainLength = 20;
var State = Categorical(2);
var Obs = Categorical(4);
var transFun = randFunction(State, State);
var obsFun = randFunction(State, Obs);

@@

var model = function() {
  return observeStates(randomValue(State), 0);
};
\end{lstlisting}
}

@@

\subsection{Latent Dirichlet allocation}
{\small
\begin{lstlisting}
var maxWordsPerDocument = 100;
var Class = Categorical(3);
var Word = Categorical(10);
var classToWord = randFunction(Class, Word);

var model = function() {
  var whichClass = randomValue(Class);
  var nWords = observe('len' + docIndex, randomIntegerERP, maxWordsPerDocument);
  repeat(nWords, function(wordIndex) {
    observe(classToWord, whichClass);
  });
};
\end{lstlisting}
}

@@

{\small
\begin{lstlisting}
var Input = Vector(30, Bool);
var Hidden = Vector(10, Bool);
var Output = Bool;

@@

var model = function() {
  var inputLayer = randomValue(Input);
  var hiddenLayer = inputToHidden(inputs[sampIndex]);
  observe(hiddenToOutput, hiddenLayer);
};
\end{lstlisting}
}
